---
title: "MachineLearning"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
print(Sys.time())
```

## R Markdown

```{r , echo=FALSE}
library(caret)
library(ggplot2)
library(kernlab)
library(e1071)
library(rattle)
library(RGtk2)
library(rpart.plot)
library(randomForest)
library(ISLR)
library(ggplot2)
library(caret)
library(gbm)
library(MASS)
```

#PART1 - Preparing Data
#Retrieving Data 
```{r , echo=TRUE}

setwd("/Users/Mood/Documents/Coursera/Machine Learning/")
training <- read.csv("pml-training.csv", na.strings = c("NA", ""))
testing <- read.csv("pml-testing.csv", na.strings = c("NA", ""))
```

#Cleaning data from unused columns 
```{r , echo=TRUE}

training <- training[, colSums(is.na(training)) == 0]
testing <- testing[, colSums(is.na(testing)) == 0]

trainData <- training[, -c(1:7)]
testData <- testing[, -c(1:7)]
```
# Creation of the Training and Validation Dataset
```{r , echo=TRUE}
set.seed(5000)
inTrain <- createDataPartition(trainData$classe, p = 0.7, list = FALSE)
train <- trainData[inTrain, ]
valid <- trainData[-inTrain, ]
```
# PART2 - Prediction
# A - Classification tree method 
#Change the k from 5 to 10 as you want)
```{r , echo=TRUE}
Path <- trainControl(method = "cv", number = 10)
fit_rpart <- train(classe ~ ., data = train, method = "rpart", trControl = Path)
print(fit_rpart, digits = 4)
```

#Doing the Prettier plot from rattle library (ClassTree)
```{r , echo=TRUE}
fancyRpartPlot(fit_rpart$finalModel)
```
#Now apply the model to the validation set (ClassTree)
```{r , echo=TRUE}
predict_rpart <- predict(fit_rpart, valid)

conf_part <- confusionMatrix(valid$classe, predict_rpart)
print(conf_part)
```
# Confirm accuracy (ClassTree)
```{r , echo=FALSE}
Accuracy_rpart <- conf_part$overall[1]
print(Accuracy_rpart)
SampleError_rpart <- paste("Sample Error = ",  1 - Accuracy_rpart)
print(SampleError_rpart)
```

# PART2 - Prediction
# B - Using the Random Forests
```{r , echo=TRUE}
fit_rf <- train(classe ~ ., data = train, method = "rf",
                trControl = Path)
print(fit_rpart, digits = 4)
```
#Now apply the model to the validation set (rf)
```{r , echo=TRUE}
predict_rf <- predict(fit_rf, valid)

conf_rf <- confusionMatrix(valid$classe, predict_rf)
print(conf_rf)
```
# Confirm accuracy (rf)
```{r , echo=FALSE}
Accuracy_rf <- conf_rf$overall[1]
print(Accuracy_rf)
SampleError_rf <- paste("Sample Error = ",  1 - Accuracy_rf)
print(SampleError_rf)

```
# PART2 - Prediction using the most reliable method
# C - Application to testing set
```{r , echo=FALSE}
Results <- predict(fit_rf, testData)
print(Results)

print(Sys.time())

```